Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-13 tex/VHzQ.tex
paths to figures changed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  %% trim=l b r t
  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z6pnt7.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used in this paper. 
    The $ZYJHK$ filter curves are from UKIRT/WFCAM.  
    The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
    The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration. 
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. }
  \label{fig:filters}
\end{figure}

@@

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Nofz/Nofz_0pnt075bins_20181211.png}
  \centering
  \vspace{-12pt}
  \caption[]
  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
    The bins are $\delta z=0.075$ in width and have the data 
    stacked on top of each other.}
  \label{fig:Nofz}
\end{figure}

@@

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_20190605.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise,
    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}
Before reporting on the detection rates, we investigate this effect
using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
by {\tt w$x$cov} the mean coverage depth, in each corresponding
band. The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3
from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular
area with a radius of 8.25'' centered on the position of this
source. For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source
Catalog
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column
Descriptions} has further details). The {\tt w$x$cov} value takes into
account e.g., individual pixels in the measurement area that may be
masked or otherwise unusable (reducing the effective pixel count and
thus the mean coverage value) as well as pixels that are affected by
distortions across the across the focal plane in single-exposure
images (where this distortion is corrected when coadding to generate
the Atlas Images). 
In the two shorter bands W1/2 we see the clear and expected
trend for brighter objects to have larger SNR, and also for the higher
signal to noise for objects with more exposures at a given
magnitude. The behaviour for the W3/4 bands is different, with two
populations clearly evident in W3 and although a bit more mixed, also
in W4. With the suggested split at SNR$>2$, and no obvious
R.A./Declination dependence seen, this behaviour is explained by the
fact that there are non-detections in W3/4 for objects (with high W1/2
SNR) that are reported in the ALLWISE catalogue.

@@

\begin{figure}
  \includegraphics[width=8.5cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
  \centering
  \caption[]
  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
    Red points are the W1 band; cyan points the W2 band.} 
  \label{fig:MIR_LC_3egs}
\end{figure}
Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
and detections there are for each VH$z$Q, while
Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR
lightcurves and associated colour changes. Here we show J0100+2802
\citep{Wu2015}, J0224-4711 and J1626+2751.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  %% trim=l b r t
  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used in this paper. 
    The $ZYJHK$ filter curves are from UKIRT/WFCAM.  
    The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
    The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration. 
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. }
  \label{fig:filters}
\end{figure}

@@

\begin{figure}
%%trim=l b r t
  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
  {../Nofz/Nofz_0pnt075bins_20181211.png}
  \centering
  \vspace{-12pt}
  \caption[]
  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
    The bins are $\delta z=0.075$ in width and have the data 
    stacked on top of each other.}
  \label{fig:Nofz}
\end{figure}

@@

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
  {../detections/WISEmag_vs_coverage_20190605.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise,
    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}
Before reporting on the detection rates, we investigate this effect
using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
by {\tt w$x$cov} the mean coverage depth, in each corresponding
band. The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3
from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular
area with a radius of 8.25'' centered on the position of this
source. For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source
Catalog
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column
Descriptions} has further details). The {\tt w$x$cov} value takes into
account e.g., individual pixels in the measurement area that may be
masked or otherwise unusable (reducing the effective pixel count and
thus the mean coverage value) as well as pixels that are affected by
distortions across the across the focal plane in single-exposure
images (where this distortion is corrected when coadding to generate
the Atlas Images). 
In the two shorter bands W1/2 we see the clear and expected
trend for brighter objects to have larger SNR, and also for the higher
signal to noise for objects with more exposures at a given
magnitude. The behaviour for the W3/4 bands is different, with two
populations clearly evident in W3 and although a bit more mixed, also
in W4. With the suggested split at SNR$>2$, and no obvious
R.A./Declination dependence seen, this behaviour is explained by the
fact that there are non-detections in W3/4 for objects (with high W1/2
SNR) that are reported in the ALLWISE catalogue.

@@

\begin{figure}
  \includegraphics[width=8.5cm]
  {../light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
  \centering
  \caption[]
  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
    Red points are the W1 band; cyan points the W2 band.} 
  \label{fig:MIR_LC_3egs}
\end{figure}
Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
and detections there are for each VH$z$Q, while
Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR
lightcurves and associated colour changes. Here we show J0100+2802
\citep{Wu2015}, J0224-4711 and J1626+2751.
